---
title: "THEMATICS - tabs"
output:
  flexdashboard::flex_dashboard:
    navbar:
      - { icon: "fa-github", href: "https://github.com/Spatial-Data-Analytics-DACSS-690D/HW1-Interactive-Visualization", align: right }

---

```{r setup, include=FALSE}
library(flexdashboard) # always
```

## Sidebar {.sidebar}

This dashboard explores the distribution of **mobile cellular subscriptions** across countries using three different mapping techniques. The data comes from the *World Indicators* dataset (WORLDINDICATORS.JSON). I focused on the region of [your chosen region, e.g., **Europe**], which includes more than 12 countries to provide meaningful comparisons.

The purpose of this dashboard is to show how different cartographic methods can highlight patterns in the same dataset:

1. **Dot Density Map (Static)**

   * Each dot represents a fixed number of mobile subscriptions.
   * Dots are randomly placed within country boundaries.
   * This helps illustrate population distribution visually, giving a sense of where mobile use is concentrated.

2. **Proportional Symbols Map (Interactive)**

   * Each country is represented with a circle symbol.
   * The size of the circle is proportional to the number of mobile subscriptions.
   * This makes it easy to quickly compare countries: larger circles = more subscriptions.

3. **Choropleth Map (Interactive)**

   * Countries are shaded according to their mobile subscription totals.
   * Darker colors indicate higher values, lighter colors indicate lower values.
   * This method provides a clean overview of regional disparities and highlights geographic trends.

By combining these three map types, the dashboard shows not just the raw numbers, but also **patterns, inequalities, and spatial relationships** in mobile technology adoption across countries.

The GitHub repository linked here contains all code, data, and steps I used to build these maps, ensuring full transparency and reproducibility.



## Column {.tabset .tabset-fade}


### DDM 1

```{r}
readRDS("plot1_a.rds")
```


### DDM 2

```{r}
readRDS("plot1_b.rds")
```

### PSM 1

```{r}
readRDS("plot2_a.rds")
```

### PSM 2

```{r}
readRDS("plot2_b.rds")
```


### CHORO 1

```{r}
readRDS("plot3_a.rds")
```

### CHORO 2

```{r}
readRDS("plot3_b.rds")
```

